The Place of the Local Group in the Cosmic Web

### 2014-08-08 paper/main.tex
algunos typo

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
}
\email{je.forero@uniandes.edu.co}

@@

All this combination of features make LG analogues rare to
find. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error fron current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters.

@@

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax
direction. However, if we look in a smaller volume below scales of
$\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with
a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb.
    \label{fig:alignment_n}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb.
    \label{fig:alignment_r}}  
\end{figure}

@@

\section*{Acknowledgements}
REG was supported by Proyecto Financiamiento Basal PFB06 and Comite Mixto ESO.

>>>>

\title{The Place of the Local Group in the Cosmic Web}
\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
  Av. Vicu\~na Mackenna 4860, Santiago, Chile
}
\email{je.forero@uniandes.edu.co}

@@

All this combination of features make LG analogues rare to
find. 
Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. 
Furthermore, if we select pairs constrained
within $2\sigma$ error from current observational measurements of the
velocity components and distance to M31, there are only $46$ systems
in a cubic volume of $250$ \hmpc side, giving a number density $\sim
1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
clusters.

@@

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax
direction. However, if we look in a smaller volume below scales of
$\sim 6$ \mpc, there is a clear alignment of the MW-M31 orbit with
a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.46\textwidth]{alignments_e1_n_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e2_n_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e3_n_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
  the Tweb.
    \label{fig:alignment_n}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.46\textwidth]{alignments_e1_r_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e2_r_all_environments.pdf} 
  \includegraphics[width=0.46\textwidth]{alignments_e3_r_all_environments.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the vector
  linking the two halos in the pair, $\hat{r}$, and the three
  eigenvectors in the Tweb.
    \label{fig:alignment_r}}  
\end{figure}

@@

\section*{Acknowledgements}
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO 3312-013-82.
The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper. The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.
